### 2022-05-15 manuscript/supplementary_information (conflicted).Rmd
AmStat round 2 revisions

```{r}
my_palette <- c("#95D840FF", "#404788FF")

@@

```{r gridOne, fig.path='figs/', fig.cap = "Whether each journal provided guidance on each of twenty statistical topics. Journals that shared publisher guidance are represented by one row (per publisher). Journals that did not offer any statistical guidance at all, or journals that referred only to guidance in external sources, are not shown. CCV = categorizing continuous variables.", fig.height = 11, fig.width = 8}
plt_one
```

```{r gridTwo, fig.path='figs/', fig.cap = "Continuation of Supplementary Figure D2.", fig.height = 11, fig.width = 8}
plt_two
```

>>>>

```{r}
# ORIGINAL GRID PLOTS 
my_palette <- c("#95D840FF", "#404788FF")

@@

```{r}
# REVISED GRID PLOTS 
my_palette <- c("#95D840FF", "#404788FF")

disciplineOrder <- sum_tab_general %>%
  filter(variable == 'guidance') %>%
  arrange(desc(percent)) %>%
  pull(esi_field)

plt_data <- d_all %>%
  #filter(has_internal_guidance == T) %>% # select journals with internal guidance
  # Recode NAs to FALSE
  mutate(across(
    starts_with('has_'), ~replace_na(., FALSE) )) %>% 
  mutate(journal = toupper(journal),
         journal = ifelse(has_publisher_guidance == T, paste0(journal,'*'), journal)) %>% # add asterisk to journals that share publisher guidance
  select(journal,esi_field,domain, starts_with("has_"), -c(has_guidance, has_internal_guidance, has_internal_guidance_section, has_external_guidance, has_publisher_guidance)) %>%
  #filter(if_any(starts_with("has"), ~ .x == TRUE)) # remove the nine journals that had no guidance on any of the 20 topics
  mutate(journal = fct_recode(journal, # shorten particularly long journal names well know by abbreviation
                              "PNAS" = "PROCEEDINGS OF THE NATIONAL ACADEMY OF SCIENCES OF THE UNITED STATES OF AMERICA",
                              "JAMA" = "JAMA-JOURNAL OF THE AMERICAN MEDICAL ASSOCIATION",
                              "THE BMJ" = "BMJ-BRITISH MEDICAL JOURNAL",
                              "JOURNAL OF ALLERGY & CLINICAL IMMUNOLOGY" = "JOURNAL OF ALLERGY AND CLINICAL IMMUNOLOGY",
                              "JOURNAL OF ALLERGY & CLINICAL IMMUNOLOGY-IN PRACTICE" = "JOURNAL OF ALLERGY AND CLINICAL IMMUNOLOGY-IN PRACTICE",
                              "INTERNATIONAL JOURNAL OF BEHAVIORAL NUTRITION & PHYSICAL ACTIVITY" = "INTERNATIONAL JOURNAL OF BEHAVIORAL NUTRITION AND PHYSICAL ACTIVITY")) %>% 
  pivot_longer(
    -c(journal,esi_field,domain),
    names_to = "topic",
    names_prefix = 'has_',
    values_to = "outcome",
    values_drop_na = FALSE
  ) %>%
  mutate(outcome = case_when(
    outcome ~ "Mentioned",
    !outcome ~ "Not mentioned",
    TRUE ~ "Not applicable (No internal guidance)"
  )) %>%
  mutate(topic_display = case_when( # create display versions of topic names
    topic == "guidance" ~ "Provides any statistical guidance",
    topic == "internal_guidance" ~ "Provides journal-specific statistical guidance",
    topic == "internal_guidance_section" ~ "Dedicated statistical guidance section",
    topic == "external_guidance" ~ "Refers to external statistical guidance",
    topic == "p_value" ~ "p values",
    topic == "significance" ~ "statistical significance",
    topic == "null_hypo" ~ "null hypotheses",
    topic == "sample_size" ~ "sample size",
    topic == "conf_int" ~ "confidence intervals",
    topic == "effect_size" ~ "effect sizes",
    topic == "multi_compare" ~ "multiple comparisons",
    topic == "subgroup" ~ "subgroup analyses",
    topic == "baseline_covar" ~ "baseline covariates",
    topic == "non_param" ~ "non-parametric tests",
    topic == "sensitivity" ~ "sensitivity analyses",
    topic == "model_assume" ~ "model assumptions",
    topic == "exclusion" ~ "data exclusions",
    topic == "outliers" ~ "outliers",
    topic == "missing" ~ "missing data",
    topic == "one_sided" ~ "one-tailed tests",
    topic == "bayes" ~ "Bayesian statistics",
    topic == "secondary" ~ "secondary outcomes",
    topic == "prespecify" ~ "prespecify analyses",
    topic == "cat_continuous" ~ "CCV",
    topic == "publisher_guidance" ~ "Shares publisher guidance"
  )) %>%
  mutate(topic_display = factor(topic_display, levels = ordered_topics), # order by n topics mentioned
         esi_field = factor(esi_field, levels = disciplineOrder), # order by discipline
         domain = factor(domain, levels = domainOrder[1:5])) # order domain

gridPlotter <- function(thisDiscipline){
  thisData <- plt_data %>% 
    filter(esi_field == thisDiscipline)

  journalOrder <- thisData %>% 
    mutate(outcome = factor(outcome),
           journal = as.character(journal),
           journal = factor(journal)) %>%
    count(journal,outcome, .drop = F) %>%
    filter(outcome == 'Mentioned') %>%
    arrange(n) %>%
    pull(journal)

  thisData %>%
    mutate(journal = factor(journal, levels = journalOrder)) %>%
    ggplot(aes(x = topic_display, y = journal)) +
      ggforce::facet_col(facets = vars(esi_field), scales = 'free_y', space = 'free') +
      geom_tile(aes(fill = outcome), colour = 'black', size = .25, alpha = .6) +
      scale_fill_manual(
        values = my_palette,
        # labels = c('Not mentioned', 'Unclear', 'Mentioned')
      ) +
      scale_x_discrete(position = 'top') +
      scale_y_discrete(labels = wrap_format(40)) + # wrap text on y axis
      theme(plot.margin = margin(0, 50, 0, 0),
            axis.ticks = element_blank(),
            axis.title.y = element_blank(),
            axis.title.x = element_blank(),
            axis.line = element_blank(),
            panel.grid.major=element_line(colour=NA),
            panel.grid.minor=element_line(colour=NA),
            legend.position = 'top',
            axis.text.x  = element_text(angle = 45, hjust = 0),
            axis.text.y  = element_text(size = 8),
            panel.background = element_blank())
}
```

```{r gridMed, fig.path='figs/', fig.cap = "Whether each Clinical Medicine journals provided guidance on each of twenty statistical topics. Topics are ordered left to right by frequency of mentions across disciplines. Disciplines, followed by journals, are ordered top to bottom by frequency of statistical guidance. CCV = categorizing continuous variables.", fig.height = 5, fig.width = 8}
gridPlotter('CLINICAL MEDICINE')
```

```{r gridMed, fig.path='figs/', fig.cap = "Continuation of Supplementary Figure D2 for the discipline of Immunology", fig.height = 5, fig.width = 8}
gridPlotter('IMMUNOLOGY')
```

```{r gridMed, fig.path='figs/', fig.cap = "Continuation of Supplementary Figure D2 for the discipline of Immunology", fig.height = 5, fig.width = 8}
gridPlotter('PSYCHIATRY & PSYCHOLOGY')
```
